---
title: "assignment_1_rmarkdown"
author: "Emil Hafeez (eh2928)"
date: "9/14/2020"
output: github_document
---
#Starting Small

This is an R Markdown file for P8105 Homework 1. I focus on meaningful naming schemas, readable code, clearly-written explanatory text, and parsimony. 

#Library Loaders Section

Let's load all the libraries we'll need to execute Assignment 1.

```{r}
library(tidyverse)
```

#Problem 1

We create a data frame which contains a random sample of size ten from a normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a factor vector of length 10 with 3 different factor levels. 

```{r}
#Load and use tibble to create aforementioned data frame
practice_df = tibble(
    vec_rnorm_numeric = rnorm(10),
    vec_greater_than_zero_logical = (vec_rnorm_numeric > 0), 
    vec_building_characters = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
    vec_temperature_factor = factor(c("Fahrenheit", "Fahrenheit", "Celsius", "Fahrenheit", "Kelvin", "Fahrenheit", "Celsius", "Kelvin", "Kelvin", "Fahrenheit"))
)

#We mean() each variable individually for illustrative purposes.
#Jeff accomplishes this in 9/15/2020 live lecture using mean(pull(practice_df, vec_rnorm_numeric)). I will test this too. 
mean(practice_df$vec_rnorm_numeric)
mean(practice_df$vec_greater_than_zero_logical) #implicitly 1's and 0's by coercion
mean(practice_df$vec_building_characters)
mean(practice_df$vec_temperature_factor)
##The numeric and logical vectors work for this, and does not for string (characters and factors) variables.
```
Now, we create a code chunk for converting variable types, propmt asks for all numeric conversions, then different conversions for different variables.
```{r echo = TRUE, results = 'hide'}
as.numeric(pull(practice_df, vec_greater_than_zero_logical))
as.numeric(pull(practice_df, vec_building_characters))
as.numeric(pull(practice_df, vec_temperature_factor))
```
Next, we implement the code converting the variable types
```{r}
as.numeric(pull(practice_df, vec_greater_than_zero_logical)) * pull(practice_df, vec_rnorm_numeric)
as.factor(pull(practice_df, vec_greater_than_zero_logical)) * pull(practice_df, vec_rnorm_numeric)
as.numeric(as.factor(pull(practice_df, vec_greater_than_zero_logical))) * pull(practice_df, vec_rnorm_numeric)
```

#Problem 2

Let's load the penguins dataset and examine the basics.
```{r}
data("penguins", package = "palmerpenguins")
penguins
head(penguins)
tail(penguins)
summary(penguins)
anyNA(penguins)
nrow(penguins)
ncol(penguins)

mean(penguins$flipper_length_mm)
mean(pull(penguins, flipper_length_mm), na.rm = TRUE)
```
This is a dataset with with 344 observations of 8 variables, and describes details about 3 species of penguin on 3 different islands; there are measurements on bill length and depth, flipper length, body mass, sex, and year, though there are missing data. 

The dataset has `r nrow(penguins)` rows (observations of penguins, it seems), and `r ncol(penguins)` columns. The mean flipper length is `r mean(pull(penguins, flipper_length_mm), na.rm = TRUE)`.

#Scatterplot
Let's make a scatterplot of the penguins' bill lengths on the x-axis and flipper lengths on the y-axis, and use color to differentiate species.

```{r}
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()
ggsave("plot_penguin_bill_and_flipper_length_by_species.pdf", height = 4, width = 4)
```