---
title: "assignment_1_rmarkdown"
author: "Emil Hafeez (eh2928)"
date: "9/14/2020"
output: github_document
---
#Starting Small

This is an R Markdown file for P8105 Homework 1. I focus on meaningful naming schemas, readable code, clearly-written explanatory text, and parsimony. 

##Library Loaders Section
```{r}
library(tidyverse)
```

#Problem 1

We create a data frame which contains a random sample of size ten from a normal distribution, a logical vector indicating whether elements of the sample are greater than 0, a character vector of length 10, and a factor vector of length 10 with 3 different factor levels. 
=
```{r}
#Load and use tibble to create aforementioned data frame
practice_df = tibble(
    vec_rnorm_numeric = rnorm(10),
    vec_greater_than_zero_logical = (vec_rnorm_numeric > 0), 
    vec_building_characters = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
    vec_temperature_factor = factor(c("Fahrenheit", "Fahrenheit", "Celsius", "Fahrenheit", "Kelvin", "Fahrenheit", "Celsius", "Kelvin", "Kelvin", "Fahrenheit"))
)
#Take the mean after each variable.

#We mean() each variable individually for illustrative purposes.
#Jeff accomplishes this in live lecture using mean(pull(practice_df, vec_rnorm_numeric)). I will test this too. 
mean(practice_df$vec_rnorm_numeric)
mean(practice_df$vec_greater_than_zero_logical) #implicitly 1's and 0's by coercion
mean(practice_df$vec_building_characters)
mean(practice_df$vec_temperature_factor)
##The numeric and logical vectors work for this, and does not for string (characters and factors) variables.
```
##Create code chunk for converting variable types, using alternative pull() command
```{r echo = true, results = 'hide'}
as.numeric(pull(practice_df, vec_greater_than_zero_logical))
as.numeric(pull(practice_df, vec_building_characters))
as.numeric(pull(practice_df, vec_temperature_factor))
```



